Precise Weed and Maize Classification through Convolutional Neuronal Networks

### 2017-10-06 Presentacion.tex
Add images

\documentclass[10pt,a4paper]{beamer}
\usepackage[utf8]{inputenc}
%\usepackage[spanish]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{makeidx}
\usepackage{graphicx}
\usepackage{makecell}
\usepackage{verbatim}
\author{Cristian Chimbo}
\usefonttheme{professionalfonts} % fuentes de LaTeX
\usetheme{Szeged}
\usecolortheme{beaver}
\setbeamercovered{transparent}
\begin{document}
%\font\myfont=cmr12 at 20pt
%\title{{\myfont Precise Weed and Maize Classification through Convolutional Neuronal Networks}}
%\author{{\bf C\'ordova Andrea\inst{1}, Barreno Mauricio, J\'acome Jos\'e }\\
%\institute{
%\inst{1}%
 % Universidad de las Fuerzas Armadas ESPE\\
 % Latacunga - Ecuador}
%{ 2nd IEEE Ecuador Technical Chapters Meeting}
%\vspace*{1cm}}
%\date{October 2017}
\title[Precise Weed and Maize Classification through Convolutional Neuronal Networks] %optional
{Precise Weed and Maize Classification through
Convolutional Neuronal Networks}

@@

@@

@@

\item Maize is one of the most important food of the world.
\item Las malas hierbas en el maiz pueden afectan hasta 5000 Kg/Hectaria de produccion.
\item La robotica esta presentando grandes avances en la agricultura de precision.
\item Inteligencia artificial cada vez se acerca mas a la inteligencia humana.\\
\section{The Propose of the present study}
\frametitle{The Propose of the present study}
\item Obtener muestras(imagenes) para conformar un dataset.
\item Segmentar las muestras.
\item Probar diferentes arquitecturas de Redes Neuronales Convolucionales para entrenar la red.
\item Hacer Benchmark en diferentes hardwares para analizar tiempos de procesamiento.
\item Optimizar la red.

@@

	\item Normalize Green Channel and then $S = 2*G - R - B$ \footnote{Poner cita aqui}

@@

	\caption{The process of image processing, por lo pronto}

@@

{Dataset Description}
\item Place Pillaro Tungurahua Ecuador
\item La imagenes fueron obtenidas encampos de maiz en su estapa inicial,( plantas con 3 a 7 hojas) \cite{sladojevic2016deep}.
\item Imagenes rotadas cada 30 para mejorar la deteccion de las planta.
\item 1/5 del total de las imagenes al azar fueron usadas para la etapa de validacion

@@

 Entrenamiento & 25695 & 8560 \\
 Validacion & 8325 & 2000 \\

@@

	\item Tested on classification of plants, poner citas

@@

@@

\caption{Comparison of the 4 types of CNN}

@@

 Iterations & 3000 & 3000 & 3000 & 3000 \\ 

@@

\section{cNET Performance}

@@

\item Obtener muestras(imagenes) para conformar un dataset.

@@

@@

\caption{Test of cNET 16 filters with optimized software}
\label{table:5}
\begin{tabular}[c c c c]{|p{2.2 cm} p{1.1cm} p{1.1cm} p{2.4cm}|} 

@@

 \textbf{Hardware } & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image}\\ 

@@

 GPU & 92.08\% & 89.11\% & 1.58 ms \\ [0.95ex]
 CPU & 92.08\% & 89.11\% & 10.92 ms \\ [0.95ex]
 CPU(Raspberry Pi) & 92.08\% & 89.11\% & 150.8 ms \\ [0.95ex]

@@

@@

\begin{tabular}[c c c c]{|p{1.0 cm} p{1.7cm} p{1.7cm} p{1.7cm}|} 

@@

@@

\item
\item
\section{Recomendations}
\frametitle{Recomendations}
\item
\item

@@

%-----------------------------
\bibliographystyle{plain}
\bibliography{bibliografiapaper}
\end{document}

>>>>

\documentclass[10pt,a4paper]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{makeidx}
\usepackage[style=verbose]{biblatex}
\usepackage{graphicx}
\usepackage{makecell}
\usepackage{verbatim}
\usefonttheme{professionalfonts} % fuentes de LaTeX
\usetheme{Szeged}
\usecolortheme{beaver}
\setbeamercovered{transparent}
\addbibresource{bibliografiapaper.bib}
\begin{document}
%\font\myfont=cmr12 at 20pt
%\title{{\myfont Precise Weed and Maize Classification through Convolutional Neuronal Networks}}
%\author{{\bf C\'ordova Andrea\inst{1}, Barreno Mauricio, J\'acome Jos\'e }\\
%\institute{
%\inst{1}%
 % Universidad de las Fuerzas Armadas ESPE\\
 % Latacunga - Ecuador}
%{ 2nd IEEE Ecuador Technical Chapters Meeting}
%\vspace*{1cm}}
%\date{October 2017}
\title[Precise Weed and Maize Classification through Convolutional Neuronal Networks] %optional
{Precise Weed and Maize Classification through
Convolutional Neuronal Networks}

@@

\logo{\includegraphics[height=1.5cm]{espe.png}}

@@

\AtBeginSection[]
{
    \frametitle{Table of Contents}
    \tableofcontents[currentsection]
}

@@

\textbf{Introduction}
\item Maize is one of the most important \textbf{food or crop?} of the world.
\item Weed can affect the maize crop up to 5000 Kg/Ha.\footnote{suarez2005distintos} %Las malas hierbas en el maiz pueden afectan hasta 5000 Kg/Hectaria de produccion.
\item Robotics has presented a huge advance in Precision Agriculture.%La robotica esta presentando grandes avances en la agricultura de precision.
\item Artificial Intelligence reached near-to-human precision.%Inteligencia artificial cada vez se acerca mas a la inteligencia humana.
\textbf{The Propose of the present study}
\item Obtain samples to conform a dataset%Obtener muestras(imagenes) para conformar un dataset.
\item Segment samples%Segmentar las muestras.
\item Test diffent network architectures of Convolutional Neural Networks for classify Maize and Weed%Probar diferentes arquitecturas de Redes Neuronales Convolucionales para entrenar la red.
\item Benchmark the best architure to analyse time of processing %Hacer Benchmark en diferentes hardwares para analizar tiempos de procesamiento.
\item Optimize the time of processing of the net%Optimizar la red.

@@

	\item Normalize Green Channel and then $S = 2*G - R - B$ \footcite{wang2013path}

@@

	\caption{The process of image processing,\textbf{ por lo pronto}}

@@

%{Dataset Description}
\item Samples obtained in Pillaro-Tungurahua-Ecuador
\item Images obtained in its initial stage(3-7 leaves) . %La imagenes fueron obtenidas encampos de maiz en su estapa inicial,( plantas con 3 a 7 hojas) 
\item Rotated images every 30º to improve detection of plants\footcite{sladojevic2016deep}%Imagenes rotadas cada 30 grados para mejorar la deteccion de las planta.
\item 1/5 of the total images chosed randomly to validate training%1/5 del total de las imagenes al azar fueron usadas para la etapa de validacion

@@

 Training & 25695 & 8560 \\
 Validation & 8325 & 2000 \\

@@

	\item Tested on classification of plants, \footcite{cheng2015feature} \footcite{potena2016fast} \footcite{di2016automatic}

@@

	\item LeNET and AlexNet(Caffe Zoo Model) \
	\item cNET and sNET \footnote{potena2016fast}
	\item 3000 iterations in each training

@@

\caption{Comparison of the 4 types of CNN in training the dataset}

@@

@@

\AtBeginSection[]
{
    \frametitle{Table of Contents}
    \tableofcontents[currentsection]
}
\section{Tuning cNET}

@@

\item cNET can be improved by decrease the number of filters
\item Images can be batched and also Caffe can be multithreaded
\item Both nets were trained with 9000 iterations

@@

\begin{table}[h]

@@

\caption{Comparison between cNET of 16 and 64 filters}
\label{table:3}
\begin{tabular}{|l c c |} 

@@

 \textbf{Parameters} & \textbf{cNET 16 filters} & \textbf{cNET 64 filters} \\ [0.75ex] 

@@

 Number of parameters & 1651376 & 6421568 \\ 
 Accuracy(\%) & 97.26 & 96.40 \\
 Loss(\%) & 8.39 & 13.72 \\ [1ex] 

@@

	\item A dataset of test with 202 images of each class was used
	\item In a single image it can be found 18 plants to classify

@@

\begin{tabular}[c c c c]{|p{1.8 cm} p{1.5cm} p{2.1cm} p{2.3cm}|} 

@@

  \textbf{Method} &\textbf{One Core} & \textbf{Multithreading} & \textbf{Multithreading} \\ 

@@

\item cNET showed the better results in classification of maize and weed
\item The reduce of the number of filters allow to decrease the processing time and increase the accuracy of the net
\item GPU showed the best results but with Multithreading and Batching CPU and Raspberry Pi can improve its time of processing 
\item Due to the limitations of the Raspberry Pi, it can't be used to classify in real time, but a Neural Module(such as Intel Movidius) can improve that result

@@

%-----------------------------
%\bibliographystyle{plain}
%\bibliography{bibliografiapaper}
\end{document}
